\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.5in,                          % specify top page margin
bottom=0.5in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin
                       
\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=6pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Chad Gauthier}

% \vspace{5pt}

% contact information
\centerline{\href{mailto:chad.gauthier32@gmail.com}{chad.gauthier32@gmail.com} | \href{https://www.github.com/cgoat24}{github.com/cgoat24}}

\vspace{-18.5pt}

% education section
\section*{Education}
\textbf{Université de Sherbrooke} -- Bachelor in Computer Science \hfill 2025 \\
\textbf{Cégep de Trois-Rivières} -- Technical degree in Computer Science \hfill 2022

\vspace{-6.5pt}

% experience section
\section*{Experience}
\textbf{Programmer-analyst intern} {Nmédia} \hfill May 2024 -- August 2024 \\
\vspace{-9pt}
\begin{itemize}
  \item Built a data analysis platform to evaluate solution performance and support data-driven decisions.
  \item Refactored and upgraded core modules to enhance codebase stability, maintainability, and performance.
  \item Collaborated in an agile team to deliver iterative improvements through sprint planning, stand-ups, and retrospectives.
\end{itemize}

\textbf{Tool programmer intern} {Ubisoft Québec} \hfill September 2023 -- December 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Engineered internal tools to automate tasks, boosting efficiency and streamlining game development workflows.
  \item Implemented features in a Go-based web app, enhancing functionality and user experience.
  \item Built end-to-end tests with Cypress to validate key user flows and ensure a high-quality codebase.
\end{itemize}

\textbf{Programmer-analyst intern} {Sherweb} \hfill January 2023 -- April 2023 \\
\vspace{-9pt}
\begin{itemize}
  \item Implemented features in a microservices app on Kubernetes, enabling scalable and resilient orchestration.
  \item Built an internal tool to streamline workflows and improve developer experience by reducing daily friction.
  \item Maintened quality assurance processes, enabling a high-quality developement process.
\end{itemize}

\textbf{Programmer-analyst} {Groupe Shift} \hfill March 2022 -- September 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Handled over 5 projects concurrently, implementing software solutions according to client requirements.
  \item Contributed to a SaaS research committee, providing insights to guide strategic product decisions.
  \item Collaborated with cross-functional teams to gather specifications, document system behavior, and validate business needs.
\end{itemize}

\vspace{-18.5pt}

% projects section
\section*{Projects}
\textbf{FlexCalc} \hfill \href{https://github.com/cgoat24/flex-calc}{github.com/cgoat24/flex-calc} \\
\vspace{-9pt}
\begin{itemize}
  \item Developed a mobile app for bodybuilding enthusiasts using Svelte, Rust and Tauri.
  \item Designed and implemented computational logic supporting a wide range of mathematical operations.
  \item Ensured a user-friendly interface and seamless integration of new features.
\end{itemize}

\textbf{TimeTunes} \hfill \href{https://github.com/cgoat24/timetunes}{github.com/cgoat24/timetunes} \\
\vspace{-9pt}
\begin{itemize}
  \item Co-developed a multiplayer mobile game where players guess song release dates by placing them on a timeline.
  \item Integrated Spotify's SDK to stream music directly within the app, enabling users to play with any public playlist.
  \item Implemented real-time multiplayer functionality, allowing users to play remotely, each on their own device.
\end{itemize}

\textbf{La Beuverie} \hfill \href{https://la-beuverie.vercel.app}{la-beuverie.vercel.app} \\
\vspace{-9pt}
\begin{itemize}
	\item Designed and developed a full-stack web application for sharing cocktail recipes, using Svelte and TypeScript.
	\item Configured Docker for local development, enabling consistent and reproducible environments.
  \item Deployed the application to Vercel, ensuring scalable and performant delivery of the web application to users.
\end{itemize}

\vspace{-18.5pt}

% skills section
\section*{Skills}
\textbf{Languages:} C\#, Javscript, Typescript, Rust, Python, Go, PHP, Java, C/C++ \\
\textbf{Frameworks/Libraries:} Vue.js, Nuxt, Svelte, Sveltekit, React, Astro, TailwindCSS, .NET, Laravel, Express.js, Hono, Prisma \\
\textbf{Databases:} SQL Server, PostgreSQL, MongoDb, MySQL \\
\textbf{Tools:} Docker, Git, Github, Gitlab, Vercel, AWS, Linux

\end{document}